Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-24 manuscript/manuscript.Rmd
readabilility, bump renv

header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{lineno}
  - \usepackage{setspace}
  - \usepackage{bookmark}
  - \usepackage{float}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage{subcaption}
  - \usepackage{tikz-cd}
  - \linenumbers
  - \doublespacing

@@

```{r}
# Collect data (outsource to separate R script later TBD)
msy <- read_csv("../data/msy.csv.gz")
ppo <- read_csv("../data/PPO250.csv.gz")
escapement <- read_csv("../data/escapement.csv.gz", show_col_types = FALSE)

# rename some columns for figure purposes:
colnames(msy) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z')
colnames(ppo) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z') 
colnames(escapement) <- c('t', 'rep', 'esc_level', 'reward', 'X', 'Y', 'Z') 
opt_escapement <- escapement |> filter(esc_level == 0.62)

best_e <- 0.62 # optimal constant escapement, computed from ../data/escapement.csv.gz
esc_sim <- escapement |> 
    pivot_longer(c("X", "Y", "Z"),
        names_to = "species", values_to = "abundance") |>
    mutate(abundance = abundance + 1)

@@

\begin{figure}
  \centering
  \includegraphics[width = 0.8\linewidth]{figures/conceptual-figure-old.png}
  \caption{
    \label{fig:conceptual}
    (A) Classical management strategies often have the common aspect of reducing the complex dynamics of the fishery ecosystem to a single equation governing the harvested population (say, $V1$). where the interaction between $V1$ and its environment is summarized to a set of parameters, such as the growth rate $r$, and the carrying capacity $K$. An advantage of one-dimensional approaches is that the optimal policy is often known exactly, and, moreover, is intuitive. For example, in the logistic equation shown, the maximal sustainable yield of the system is attained at K/2. (B) RL allows us to solve for quantitative decision strategies considering more complex ecosystem dynamics. For example, in this paper, we find harvest strategies for a three-species model using a model-free RL algorithm, PPO. (C) We show how the RL-based solution that considers all three species finds harvest policies with higher average reward and with (D) lower probability of harvest species collapse than the classical approaches, only considering the dynamics of V1.
  }
\end{figure}

<!--
```{r conceptual, echo = FALSE, message=FALSE, fig.align='center', fig.cap='(A) Classical management strategies often have the common aspect of reducing the complex dynamics of the fishery ecosystem to a single equation governing the harvested population (say, $V1$). where the interaction between $V1$ and its environment is summarized to a set of parameters, such as the growth rate $r$, and the carrying capacity $K$. An advantage of one-dimensional approaches is that the optimal policy is often known exactly, and, moreover, is intuitive. For example, in the logistic equation shown, the maximal sustainable yield of the system is attained at K/2. (B) RL allows us to solve for quantitative decision strategies considering more complex ecosystem dynamics. For example, in this paper, we find harvest strategies for a three-species model using a model-free RL algorithm, PPO. (C) We show how the RL-based solution that considers all three species finds harvest policies with higher average reward and with (D) lower probability of harvest species collapse than the classical approaches, only considering the dynamics of V1.', out.width='1\\linewidth', fig.pos='H'}
knitr::include_graphics("Figures/conceptual-figure-old.png")
```
-->

@@

\begin{align}
  \label{eq:general model}
  \Delta N_t := N_{t+1} - N_t = f(N_t) - F^T N_t,
\end{align}
where $N_t = (X_t,\ Y_t,\ \dots) \in \mathbb{R}^{n}_+$ is a vector of populations, $f:\mathbb{R}^{n}\to\mathbb{R}^{n}$ is an arbitrary function, where the product of the mortality and the stock size, $F^T N_t$ is the harvest size at timestep $t$. 
Here, $F\in\mathbb{R}^n$ is a vector of fishing intensities, where $F_i$ is the intensity with which the $i$-th species is fished.
We will focus on the case where only the first species is fished, $F= (F_1,\ 0,\ \dots,\ 0)$.

@@

\begin{align}
  \label{eq:logistic}
  f(X_t) = r X_t\big(1 - X_t / K \big) =: L(X_t;\ r, K).
\end{align}

The model this $f$ gives rise to is known as the Gordon-Schaefer model, after foundational work which first developed the concept of maximum sustainable yield, MSY, [@Gordon1954; @Schaefer1954], which remains a central concept in fisheries management.
In this model, the maximum growth rate occurs at population size of $N = K/2$.
This value is approached asymptotically, from any positive initial state $N_0 \in (0,K)$, under a constant mortality $F = r/2$ policy.
At equilibrium this produces an asymptotic harvest of $rK/4$ per time step---the maximum yield sustainable indefinitely.

@@

\begin{align}
  \label{eq:may}
  f_{\text{May}}(X_t)
  := L(X_t;\ r, K) - F(X_t, H; \beta,c),
\end{align}
where,
\begin{align*}
  F(X_t,H;\ \beta,c) := \frac{\beta H X_t^2}{c^2 + X_t^2}.
\end{align*}

@@

Eq. \eqref{eq:may} is an interesting study case of a *tipping point* (saddle-node bifurcation) (see Fig. \ref{fig:may stable}).
Holding the value of $\beta$ fixed, for intermediate values of $H$ there exist two stable fixed points for the state $\hat X_t$ of the system, these two attractors separated by an unstable fixed point.
At a certain threshold value of $H$, however, the top stable fixed point collides with the unstable fixed point and both are annihilated.
For this value of $H$, and for higher values, only the lower fixed point remains.
This also creates the phenomenon of *hysteresis*, where returning $H$ to its original value is not sufficient to restore $\hat X_t$ to the original stable state.

\begin{figure}
  \centering
  \includegraphics[width = 0.8\linewidth]{figures/MayStablePoints.pdf}
  \caption{
    \label{fig:may stable}
    The fixed point diagram for the model \cite{may77} associated to $f_{\text{May}}$ as a function of varying the parameter $\beta H$.
    That is, these are the zeroes of the function $f_{\text{May}}$. 
    Stable fixed points (also known as *attractors*) are plotted using a solid line, while the unstable fixed point is shown as a dotted line.
  }
\end{figure}

@@

\begin{align}
\label{eq:3d model}
\begin{split}
  \Delta X_t &= L(X_t;\ r_X, K_X) - F(X_t, Z_t;\ \beta, c) - c_{XY}X_tY_t - h_t,\\
  \Delta Y_t &= L(Y_t;\ r_Y, K_Y) - D F(Y_t, Z_t;\ \beta, c) - c_{XY}X_tY_t,\\
  \Delta Z_t &= \left(f(X_t + DY_t\right) - d_Z)Z_t.
\end{split}
\end{align}
The model is conceptualized in Fig. \ref{fig:conceptual}, panel B.
It contains three populations, the state at time $t$ is $(X_t, Y_t, Z_t)$. 
Species $Z$ preys on both $X$ and $Y$, while the latter two compete for resources.
There are ten parameters in this model: 
The growth rate and carrying capacity, $r_X$, $K_X$, $r_Y$ and $K_Y$, of $X$ and $Y$.
A parameter $c_{XY}$ mediating a Lotka-Volterra competition between $X$ and $Y$.
A maximum hunting intensity $\beta$ and half-maximum $c$ specifying how $Z$ forages on $X$ and $Y$.
A parameter $D$ regulating a relative preference of $Z$ to prey on $Y$.
Finally, a death rate $d_Z$ and a parameter $f$ related to the birth rate of $Z$.

@@

We have, up to now, presented eqs. \eqref{eq:may} and \eqref{eq:3d model} as *deterministic* dynamical models for the sake of clarity.
In practice, we will consider a stochastic contribution to these dynamics.
This way, instead of eq. \eqref{eq:may}, we consider the following stochastic single-species system
\begin{align}
  \label{eq:may stoch}
  \Delta X_t
  = L(X_t;\ r, K) - F(X_t, H; \beta,c) - h_t + \eta_t,
\end{align}
where $\{\eta_t\}_t$ are independent Gaussian variables with zero mean.
The variance $\sigma^2$ of $\eta_t$ is an additional parameter of the model.

Similarly, we use the following dynamical model in place of eq. \eqref{eq:3d model}
\begin{align*}
  \label{eq:3d model stoch}
  \begin{split}
    \Delta X_t &= L(X_t;\ r_X, K_X) - F(X_t, Z_t;\ \beta, c) - c_{XY}X_tY_t - h_t + \eta_{X,t},\\
    \Delta Y_t &= L(Y_t;\ r_Y, K_Y) - D F(Y_t, Z_t;\ \beta, c) - c_{XY}X_tY_t + \eta_{Y,t},\\
    \Delta Z_t &= \left(f(X_t + DY_t\right) - d_Z)Z_t + \eta_{Z,t}.
\end{split}
\end{align*}
Here, again, $\{\eta_{i,t}\}$ is a set of independent Gaussian variables centered at zero with variances, respectively, $\sigma_X^2$, $\sigma_Y^2$ and $\sigma_Z^2$.

```{r classical_tuning, fig.cap = "TBD.  Red = MSY, Green = 0.8 TAC", out.width = "6.5in"}
msy_rewards <- msy |>
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

esc_rewards <- escapement |>
  group_by(esc_level, rep) |>
  filter(t == max(t)) |> 
  group_by(esc_level) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

rmsy <- msy_rewards |>
  ggplot(aes(action, mean_reward, 
             ymin = mean_reward - 2*sd,
             ymax=mean_reward+2*sd)) +
  geom_point() + geom_ribbon(alpha=0.4) +
  labs(y = "episode reward", x = "constant mortality") +
  theme(aspect.ratio = 1/1) + 
  geom_vline(aes(xintercept=0.0465), color="red") + 
  geom_vline(aes(xintercept=0.0370), color="green")

resc <- esc_rewards |>
  ggplot(aes(esc_level, mean_reward, 
             ymin = mean_reward - 2*sd,
             ymax=mean_reward+2*sd)) +
  geom_point() + geom_ribbon(alpha=0.4) +
  labs(y = "episode reward", x = "constant escapement") +
  theme(aspect.ratio = 1/1)

(rmsy | resc)
```

@@

Here we review classical strategies for sustainable fishery management and we provide a birds-eye view of the alternative approach we propose.
A summary of the contrast between the two strategies is given in Fig. \ref{fig:decision approaches}.

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/DecisionApproaches.pdf}
  \caption{
  \label{fig:decision approaches}
  TBD.
  }
\end{figure}

@@

There are several strategies that have been used to manage fisheries: *escapement*, *maximum sustainable yield (MSY)*, *total allowable catch (TAC)*, among others.
We collectively refere to these as *classical*, and will compare their performance to RL-based management strategies.
Classical strategies derive an optimal harvest policy using a simple model for the system dynamics.
While often complex models of the ecosystem are used to estimate the fish population of interest (i.e. $X_t$), the quota is set only taking into account the estimate $X_t$.
The function determining this quota is derived from a simple dynamical model for the population (see text box 1).

\textbf{Text box 1 (TBD formatting)}
Let us consider a ubiquitous simple example: an MSY policy based on a logistic growth model for $X_t$ (see eqs. \eqref{eq:general model} and \eqref{eq:logistic}).

Classical strategies have the common aspect of reducing the complex dynamics of the fishery ecosystem to a single equation governing the harvested population (say, $F$). 
A common example is using a logistic growth equation,
$$
  F_{t+1} - F_t = r F_t( 1 - F_t / K) - h_t =: L(F_t) - h_t,
$$
where the interaction between $F$ and its environment is summarized to two parameters, the growth rate $r$, and the carrying capacity $K$.
In the equation above, $h_t$ is the *harvest* at timestep $t$.
The goal is to choose the harvest policy $h:F_t\mapsto h_t$ such that long-term profits are maximized.

@@

Our results suggest that DRL can find solutions that are more sustainable *and* more profitable than any constant mortality strategy.
Indeed, DRL finds solutions in which, for certain periods of time, no harvest is performed on the system.
These periods effectively allow the system to, in a sense, "reset" itself.
They lead to a distinctive oscillating behavior of the system state over time, with periods of relative depletion followed by periods of growth. 
Figure TBD exemplifies this point by comparing one times series of the system state obtained using each of these policies.

```{r timeseries, fig.cap="TBD.", out.width = "6.5in"}
policy_labels <- list("msy" = "Opt. Const. Mortality", "tac"= "80% Opt. Const. Mortality", "ppo"= "DRL")
policy_labeller <- function(variable,value){
  return(policy_labels[value])
}
msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(rep == 0) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 2/3)
```

@@

(p1 / p2) + plot_annotation(tag_levels = 'A')
```

```{r state-space, fig.cap="TBD.", out.width = "6.5in"}
i_tac <- which.min(abs(actions - best_action * 0.8))

# color pallette limits
library(RColorBrewer)
myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(0,0.25))

pmsy <- msy |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  filter(action == best_action) |>
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  ggtitle("Opt. Const. Mortality")

ptac <- msy |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  filter(action == actions[[i_tac]]) |>
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  ggtitle("80% Opt. Const. Mortality")

pppo <- ppo |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  ggtitle("DRL")

pesc <- opt_escapement |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, 
        harvest = case_when(
          X - esc_level > 0 ~ X - esc_level,
          X - esc_level <= 0 ~  0)
         ) |> 
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  ggtitle("Opt. Const. Escapement")

(
  (pmsy | ptac) / (pppo | pesc) +
  plot_layout(guides = "collect") & theme(legend.position = 'right')
) + 
  plot_annotation(tag_levels = c('A'))
```

**Probably more for the discussion**
It is well known that following MSY policies can lead to over-fishing.
Our results reproduce this behavior and, furthermore, warn that using a TAC policy instead might not be enough to gain sustainability.
Figure \ref{rew_len_fig}-A summarizes episode length distribution for MSY, TAC and DRL.
While the DRL-derived policy does not lead to extinctions, both MSY and TAC do so, and thus their episode mean length is lower than the maximal episode length (in our case set at 200 years).
This difference is reflected on the profits earned by the agent, as shown in Fig. TBD-B.

>>>>

header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{lineno}
  - \usepackage{setspace}
  - \usepackage{bookmark}
  - \usepackage{float}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage{subcaption}
  - \linenumbers
  - \doublespacing

@@

@@

```{r}

#| label: conceptual
#| echo: FALSE
#| message" FALSE
#| fig.align: 'center'
#| fig.cap: '(A) Classical management strategies often have the common aspect of reducing the complex dynamics of the fishery ecosystem to a single equation governing the harvested population (say, $V1$). where the interaction between $V1$ and its environment is summarized to a set of parameters, such as the growth rate $r$, and the carrying capacity $K$. An advantage of one-dimensional approaches is that the optimal policy is often known exactly, and, moreover, is intuitive. For example, in the logistic equation shown, the maximal sustainable yield of the system is attained at K/2. 
#| (B) RL allows us to solve for quantitative decision strategies considering more complex ecosystem dynamics. For example, in this paper, we find harvest strategies for a three-species model using a model-free RL algorithm, PPO. 
#| (C) We show how the RL-based solution that considers all three species finds harvest policies with higher average reward and with (D) lower probability of harvest species collapse than the classical approaches, only considering the dynamics of V1.', 
#| out.width: '1\\linewidth', 
#| fig.pos: 'H'

knitr::include_graphics("Figures/conceptual-figure.png")
```

@@

\begin{align}
  \label{eq:general model}
  N_{t+1} - N_t = f(N_t) - F N_t := \Delta N_t,
\end{align}
where $N_t = (X_t,\ Y_t,\ \dots) \in \mathbb{R}^{n}_+$ is a vector of populations, $f:\mathbb{R}^{n}\to\mathbb{R}^{n}$ is an arbitrary function, where the product of the mortality and the stock size, $F N_t$ is the harvest size at timestep $t$.

@@

$$
  f(X_t) = r X_t\big(1 - X_t / K \big) =: L(X_t;\ r, K).
$$
Which combined with the harvest term from \eqref(eq:general model) is known as the Gordon-Schaefer model, after foundational work which first developed the concept of maximum sustainable yield, MSY, [@Gordon1954; @Schaefer1954], which remains a central concept in fisheries management.  
In this model, note that the maximum growth rate occurs at population size of $N = K/2$, which is approached asymptotically from any positive initial state $N_0 \in (0,K)$ under a constant mortality of $F = r/2$, which thus produces a harvest of $rK/4$ at equilibrium -- the maximum yield sustainable indefinitely.

@@

\begin{align}
  \label{eq:may}
  f(X_t)
  = L(X_t;\ r, K) - F(X_t, H; \beta,c),
\end{align}
where,
\begin{align*}
  F(X_t,H;\ \beta,c) := \frac{\beta H X_t^2}{c^2 + X_t^2}.
\end{align*}

@@

Eq. \eqref{eq:may} is an interesting study case of a *tipping point* (saddle-node bifurcation) (see Fig. \ref{tbd}).
Holding the value of $\beta$ fixed, for intermediate values of $H$ there exist two stable fixed points for the state $\hat X_t$ of the system, these two attractors separated by an unstable fixed point.
At a certain threshold value of $H$, however, the top stable fixed point collides with the unstable fixed point and both are annihilated.
For this value of $H$, and for higher values, only the lower fixed point remains.
This also creates the phenomenon of *hysteresis*, where returning $H$ to its original value is not sufficient to restore $\hat X_t$ to the original stable state.

@@

\begin{align}
\label{eq:3d model}
\begin{split}
  \Delta X_t &= L(X_t;\ r_X, K_X) - F(X_t, Z_t;\ \beta, c) - c_{XY}X_tY_t - h_t,\\
  \Delta Y_t &= L(Y_t;\ r_Y, K_Y) - D F(Y_t, Z_t;\ \beta, c) - c_{XY}X_tY_t,\\
  \Delta Z_t &= \left(f(X_t + DY_t\right) - d_Z)Z_t.
\end{split}
\end{align}
The model is conceptualized in Fig. \ref{fig:tbd}.
It contains three populations, the state at time $t$ is $(X_t, Y_t, Z_t)$. 
Species $Z$ preys on both $X$ and $Y$, while the latter two compete for resources.
There are ten parameters in this model: 
The growth rate and carrying capacity, $r_X$, $K_X$, $r_Y$ and $K_Y$, of $X$ and $Y$.
A parameter $c_{XY}$ mediating a Lotka-Volterra competition between $X$ and $Y$.
A maximum hunting intensity $\beta$ and half-maximum $c$ specifying how $Z$ forages on $X$ and $Y$.
A parameter $D$ regulating a relative preference of $Z$ to prey on $Y$.
Finally, a death rate $d_Z$ and a parameter $f$ related to the birth rate of $Z$.

@@

\textbf{Probably just merge on previous sections.}
We consider a stochastic contribution to the system's dynamics.
This way, eq. \eqref{eq:may} becomes
\begin{align}
  \label{eq:may stoch}
  \Delta X_t
  = L(X_t;\ r, K) - F(X_t, H; \beta,c) - h_t + \eta_t,
\end{align}
where $\{\eta_t\}_t$ are independent Gaussian variables with zero mean.
The variance $\sigma^2$ of $\eta_t$ is an additional parameter of the model.

Similarly, eq. \eqref{eq:3d model} becomes
\begin{align*}
  \label{eq:3d model stoch}
  \begin{split}
    \Delta X_t &= L(X_t;\ r_X, K_X) - F(X_t, Z_t;\ \beta, c) - c_{XY}X_tY_t - h_t + \eta_{X,t},\\
    \Delta Y_t &= L(Y_t;\ r_Y, K_Y) - D F(Y_t, Z_t;\ \beta, c) - c_{XY}X_tY_t + \eta_{Y,t},\\
    \Delta Z_t &= \left(f(X_t + DY_t\right) - d_Z)Z_t + \eta_{Z,t}.
\end{split}
\end{align*}

@@

Here we review classical strategies for sustainable fishery management and we provide a birds-eye view of the alternative approach we propose.
A summary of the contrast between the two strategies is given in Fig. \ref{tbd}.

@@

There are several strategies that have been used to manage fisheries: *escapement*, *maximum sustainable yield (MSY)*, *total allowable catch (TAC)*, among others.
We collectively refere to these as *classical*, and will compare their performance to RL-based management strategies.
As shown in Fig. \ref{fig:tbd}, classical strategies have the common aspect of reducing the complex dynamics of the fishery ecosystem to a single equation governing the harvested population (say, $F$). 
A common example is using a logistic growth equation,
$$
  F_{t+1} - F_t = r F_t( 1 - F_t / K) - h_t =: L(F_t) - h_t,
$$
where the interaction between $F$ and its environment is summarized to two parameters, the growth rate $r$, and the carrying capacity $K$.
In the equation above, $h_t$ is the *harvest* at timestep $t$.
The goal is to choose the harvest policy $h:F_t\mapsto h_t$ such that long-term profits are maximized.

@@

```{r}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, 
                      warning = FALSE, fig.height=5, fig.width=7.5)
msy <- read_csv("../data/msy.csv.gz")
ppo <- read_csv("../data/PPO250.csv.gz")
escapement <- read_csv("../data/escapement.csv.gz", show_col_types = FALSE)

# rename some columns for figure purposes:
colnames(msy) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z')
colnames(ppo) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z') 
colnames(escapement) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z')

best_e <- 0.62 # optimal constant escapement, computed from ../data/escapement.csv.gz
esc_sim <- escapement |> 
    rename(escapement = action) |> # data had a naming problem
    filter(escapement == best_e) |> 
    pivot_longer(c("X", "Y", "Z"),
        names_to = "species", values_to = "abundance") |>
    mutate(abundance = abundance + 1)

Our results suggest that DRL can find solutions that are more sustainable *and* more profitable than any constant mortality strategy.
Indeed, DRL finds solutions in which, for certain periods of time, no harvest is performed on the system.
These periods effectively allow the system to, in a sense, "reset" itself.
They lead to a distinctive oscillating behavior of the system state over time, with periods of relative depletion followed by periods of growth. 
Figure \ref{fig:tbd} exemplifies this point by comparing one times series of the system state obtained using each of these policies.

```{r timeseries_fig, fig.cap="TBD.", out.width = "6.5in"}
policy_labels <- list("msy" = "Opt. Const. Mortality", "tac"= "80% Opt. Const. Mortality", "ppo"= "DRL")
policy_labeller <- function(variable,value){
  return(policy_labels[value])
}
msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(rep == 0) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 2/3)
```

@@

(p1 / p2)
```

**Probably more for the discussion**
It is well known that following MSY policies can lead to over-fishing.
Our results reproduce this behavior and, furthermore, warn that using a TAC policy instead might not be enough to gain sustainability.
Figure TBD-A summarizes episode length distribution for MSY, TAC and DRL.
While the DRL-derived policy does not lead to extinctions, both MSY and TAC do so, and thus their episode mean length is lower than the maximal episode length (in our case set at 200 years).
This difference is reflected on the profits earned by the agent, as shown in Fig. TBD-B.
